---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Packages needed for the assignment

```{r, echo = TRUE}
library(ggplot2)
library(timeDate)
```

## Loading and preprocessing the data
```{r, echo=TRUE}
fileurl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(fileurl,destfile="factivity.zip",method="curl")
unzip("factivity.zip")

code <- read.csv("activity.csv")
head(code,10)
```

## What is mean total number of steps taken per day?
Step 1: summarize number of step per day
```{r, echo=TRUE}
agg_steps <- aggregate(code$steps,by = list(day=code$date),FUN=sum, na.rm=TRUE)

```

Step 2: plot a histogram
```{r, echo = TRUE}
qplot(x,data=agg_steps,weight=as.numeric(day), geom="histogram",binwidth=500,ylab = "Frequency used",xlab = "Total steps per day")

```

## Mean and median number of steps taken each day
```{r, echo = TRUE}
mean <- mean(agg_steps$x)
mean
median <- median(agg_steps$x)
median
```


## What is the average daily activity pattern?

## Time series plot of the average steps taken per 5 minutes interval

```{r, echo = TRUE}
avg_per_interval <- aggregate(x=code$steps,by=list(code$interval),FUN = mean, na.rm=TRUE)
avg_steps <- ggplot(data=avg_per_interval, aes(x=Group.1, y=x))+ geom_line() + ylab("avg steps taken") + xlab("5 miutes interval")
avg_steps
```

## Identify the 5 minutes interval than on average contains the maximum number of steps

```{r, echo = TRUE}
max_steps <- max(avg_per_interval$x)
max_steps
max_interval <- subset(avg_per_interval, x==max_steps)
max_interval
```


## Imputing missing values

```{r, echo = TRUE}
number_of_na <- length(which(is.na(code$steps)))
code2 <- code
head(code2,10)
code2$steps[is.na(code2$steps)] <- round(mean(code2$steps, na.rm=TRUE))
head(code2,10)
```

## Histogram of new dataframe
```{r, echo = TRUE}
agg_steps2 <- aggregate(code2$steps,by = list(day=code2$date),FUN=sum, na.rm=TRUE)
qplot(x,data=agg_steps2,weight=as.numeric(day), geom="histogram",binwidth=500,ylab = "Frequency used",xlab = "Total steps per day")
```
### Mean and median of new dataframe
```{r, echo = TRUE}
mean2 <- mean(agg_steps2$x)
mean2
median2 <- median(agg_steps2$x)
median2
```

## Are there differences in activity patterns between weekdays and weekends?
```{r, echo = TRUE}
code3 <- code2
code3["Weekdays"] <- NA
head(code3,10)
code3$Weekdays <- isWeekday(code$date, wday=1:5)
head(code3,10)
```
### weekdays dataframe and graph
```{r, echo = TRUE}
weekday_dataframe <- subset(code3, code3$Weekdays==TRUE)
wd_df <- aggregate(x=weekday_dataframe$steps,by=list(weekday_dataframe$interval),FUN = mean, na.rm=TRUE)
wd_df_plot <- ggplot(data=wd_df, aes(x=Group.1, y=x))+ geom_line() + ylab("avg steps taken") + xlab("5 miutes interval")
wd_df_plot
```
### weekend dataframe and graph
```{r, echo = TRUE}
weekend_dataframe <- subset(code3,code3$Weekdays==FALSE)
we_df <- aggregate(x=weekend_dataframe$steps,by=list(weekend_dataframe$interval),FUN = mean, na.rm=TRUE)
we_df_plot <- ggplot(data=we_df, aes(x=Group.1, y=x))+ geom_line() + ylab("avg steps taken") + xlab("5 miutes interval")
we_df_plot
```
